A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
move todo

In this section we briefly summarize balance equations of fine-strain hyperelastic continuum in Lagrangian (also known as referential) description.

{\color{red}
TODO: JP please adjust this part to your liking
}

@@

{\color{red}TODO: linearize and show how tangent look like.
Also show what it boils down in the case of small strain.
}

>>>>

@@

{\color{red}TODO: JP add the linearization and material/geometric tangents.
}
